Wigglyhedra

### 2024-11-15 FPSAC25/wigglyhedraFPSAC.tex
update affiliation and grants
improve last section

%% then use \addressmark to match authors to institutions here
\address{
	\addressmark{1}The Australian National University, Canberra, Australia \\ 
	\addressmark{2}Universitat de Barcelona \& Centre de Recerca Matemàtica, Spain
}

@@

\begin{proposition}
\label{prop:hn-filtration}
  Let \(X \in \mathcal{C}_{n+1}\) be a spherical object.
  Consider the set of all indecomposable summands of the nonzero objects \(H^j(X)\).
  Let \(T\) be the corresponding set of wiggly arcs.
  Then
  \begin{compactenum}
  \item 
    \(T\) is a subset of a wiggly pseudotriangulation.
  \item \(T\) contains at most one of the two irrelevant wiggly arcs.
  \end{compactenum}
\end{proposition}
\begin{proposition}
\label{prop:ext1}
Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\).
Then the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\Ext_{\mathcal{A}_m}^1(X,X')\).
Thus \(\alpha\) and \(\alpha'\) are compatible (as in~\cref{def:compatible}) if and only if \({\Ext_{\mathcal{A}_m}^1(X, X') = 0}\).
%\vincent{Do you mean \cref{def:compatible} here?}
\end{proposition}

>>>>

%% then use \addressmark to match authors to institutions here
\address{
	\addressmark{1}The Australian National University, Canberra, Australia \\ 
	\addressmark{2}Universitat de Barcelona \& Centre de Recerca Matemàtica, Barcelona, Spain
}

@@

For a general object \(X\) of \(\mathcal{C}_m\), the indecomposable factors of the cohomology filtration can be arbitrary.
However, the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
This categorical interpretation of the pseudotriangulations was our initial motivation to study the wiggly complex.

\begin{proposition}
\label{prop:hn-filtration}
  Let \(X \in \mathcal{C}_{n+1}\) be a spherical object.
  Consider the set of all indecomposable summands of the nonzero objects \(H^j(X)\).
  Let \(T\) be the corresponding set of wiggly arcs.
  Then
  \begin{compactenum}
  \item 
    \(T\) is a subset of a wiggly pseudotriangulation.
  \item \(T\) contains at most one of the two irrelevant wiggly arcs.
  \end{compactenum}
\end{proposition}

We finally give a categorical interpretation of the compatibility (see~\cref{def:compatible}) and incompatibility degree (see~\cref{def:incompatibilityDegree}) of two arcs.

\begin{proposition}
\label{prop:ext1}
Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\).
Then the incompatibility degree of \(\alpha\) and \(\alpha'\)  is the dimension of~\(\Ext_{\mathcal{A}_m}^1(X,X')\).
Thus \(\alpha\) and \(\alpha'\) are compatible if and only if~\({\Ext_{\mathcal{A}_m}^1(X, X') = 0}\).
%\vincent{Do you mean \cref{def:compatible} here?}
\end{proposition}
